Leadership across cultures and contexts: an exploratory analysis

### 2020-04-02 leadership_across_cultures_contexts.Rmd
Added analysis of female co-authors and female leadership

>>>>

## Effects of document meta-data on leadership patterns

```{r tabauthorgender}
unique_authors <- unique(authorship[c('author_ID', 'author_gender')])
tab_author_gender <- table(unique_authors$author_gender)
mm_coauthorSUM <- summary(mm_coauthor)
mm_coauthorP <- mm_coauthorSUM$coefficients['female_coauthorTRUE', 'Pr(>|z|)']
```

We explored whether document features, such as date of publication and gender of authors, influenced reporting of leader functions and qualities. There were `r tab_author_gender['male']` male authors, `r tab_author_gender['female']` females authors, and `r tab_author_gender['unkown']` authors whose gender we could not determine; some of these authors were co-authors. We then tested if text records with a female author or co-author were more likely to discuss female leaders. Of the `r sum(tab_coauthor['FALSE',])` text records with no female co-author, `r tab_coauthor['FALSE','yes']` (`r 100*signif(tab_coauthor['FALSE','yes']/sum(tab_coauthor['FALSE',]),2)`%) reported female leadership. Of the `r sum(tab_coauthor['TRUE',])` text records with female co-author, on the other hand, `r tab_coauthor['TRUE','yes']` (`r 100*signif(tab_coauthor['TRUE','yes']/sum(tab_coauthor['TRUE',]),2)`%) reported female leadership, suggesting that female ethnographers were more likely to report female leaders. However, after accounting for the non-independence of text records (i.e., multiple records from the same document) using a logistic mixed effects regression model, we found that although there was a positive effect of co-author gender on reporting female leadership (OR = `r signif(mm_coauthorOR, 2)`), it was not statistically significant (p = `r signif(mm_coauthorP, 2)`).
